Stack Safety is a Security Property

### 2021-04-15 tex/main.tex
Update enforcement with current example

Example \ref{fig:passingsimple} shows a sample trace of
a program that passes a value on the stack, without an attack.
We extend our call annotation with an additional parameter identifying a memory location to be
passed, and our diagram displays it in magenta. Our notion of domains is extended as well,
to include \(\passed{\depth,\depth'}\), recording two depths. We note the
current depth of the active function next to the stack pointer in the diagram, for reference.
The argument {\tt a} has
its value copied from {\tt x}, and we note that {\tt f} can read it -- because it is marked
as passed between depths 0 and 1, it is not varied. Then at instruction 13 it is even
modified, and naturally this is permitted as well.

@@

Note that in this policy both the entry and exit sequences
must write to each element of
the frame, which can be quite expensive, especially for programs that
allocate large but sparsely populated frames; we return to this point
in \cref{sec:lazy}.
%
The running example in \cref{fig:running-trace-a} manages the stack in this way.
For example, {\tt f}'s ``blessed'' sequences allocate space to save its return
address (and private variables) in instructions 20--21, and later restores that
return address and deallocates its private frame space before returning in
34--36. Additionally, unlike in the simplified presentation of the policy, the
caller passes information to the callee through the stack, and for this creates
and initializes (22 and 24--25) and destructs (29) the argument part of the
callee's stack frame.\rb{The policy would also need to control this, I think it
  is clear}
\rb{TODO: References to the running example are no longer valid! We could use
figures 5 or 6, referencing the figures, not the invisible assembly code.}
%
%\rb{Note that we have also considered and implemented more flexible schemes
%  based on allowing operations above the current activation depth. How do we put
%  these together?}
%\rb{Do we want to discuss variations involving frame pointers or more implicit
%  return addresses, argument passing on the stack, alloc/dealloc, etc.?}
%\rb{Where to talk about the role of the compiler?}

>>>>

Example~\ref{fig:passingsimple} shows a sample trace of
a program that passes a value on the stack, without an attack.
We extend our call annotation with an additional parameter identifying a memory location to be
passed, and our diagram displays it in magenta. Our notion of domains is extended as well,
to include \(\passed{\depth,\depth'}\), recording two depths. We note the
current depth of the active function next to the stack pointer in the diagram, for reference.
The argument {\tt a} has
its value copied from {\tt x}, and we note that {\tt f} can read it -- because it is marked
as passed between depths 0 and 1, it is not varied. Then at instruction 13 it is even
modified, and naturally this is permitted as well.

@@

Note that in this policy both the entry and exit sequences
must write to each element of
the frame, which can be quite expensive, especially for programs that
allocate large but sparsely populated frames; we return to this point
in \cref{sec:lazy}.
%
For example, the program in \cref{fig:passingsimple} manages the stack
in this way. Here, the call pseudo-instruction to {\tt f} in line 5
hides a blessed sequence of instructions that allocate space to save
its return address to {\tt main} and seal the protected part of the
stack before {\tt f}'s body starts executing at 10. Conversely, the
return instruction in line 15 restores and jumps to the return address
and deallocates its frame space, and unseals the corresponding parts
of the stack. The function itself allocates and deallocates its own
private frame space in instructions 10 and 14. Additionally, unlike in
the simplified presentation of the policy, the caller shares the
arguments passed to the callee through the stack, and for this creates
and initializes (3--4) and destructs (6) the argument part of the
callee's stack frame.
%
%\rb{Note that we have also considered and implemented more flexible schemes
%  based on allowing operations above the current activation depth. How do we put
%  these together?}
%\rb{Do we want to discuss variations involving frame pointers or more implicit
%  return addresses, argument passing on the stack, alloc/dealloc, etc.?}
%\rb{Where to talk about the role of the compiler?}
